ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
Fix weirdness of lists of attributes
Add Appveyor to CI section

In addition, specific fields from the \pybox|Reference| and \pybox|Apparatus|
attributes can be included by specifying the name after a colon. These options
are:
%
\noindent\begin{itemize*}
    \item \pybox|'Reference:Volume'|
    \item \pybox|'Reference:Journal'|
    \item \pybox|'Reference:DOI'|
    \item \pybox|'Reference:Authors'|
    \item \pybox|'Reference:Detail'|
    \item \pybox|'Reference:Year'|
    \item \pybox|'Reference:Pages'|
    \item \pybox|'Apparatus:Kind'|
    \item \pybox|'Apparatus:Facility'|
\end{itemize*}

% This weirdness is necessary to prevent the list from running over the margin
\noindent\begin{itemize*}
    \item \pybox|'Apparatus:Institution'|
\end{itemize*}

@@

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for automated testing, and currently has
100\% line and branch coverage for all executable code in the repository. This
means that the tests execute every line of code at least once, and evaluate
every branch statement (e.g., if-then-else statements) to execute every condition
at least once.
Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} provides continuous
integration service, including running the test suite, building and distributing binary
installer packages, and building and publishing the online documentation. This automation
runs the test suite after every change to the source code, keeps the documentation
up-to-date with the latest changes, and streamlines the release of new versions.

>>>>

In addition, specific fields from the \pybox|`Reference'| and \pybox|`Apparatus'|
columns can be included by specifying the name after a colon. These options
are:
%
\noindent\begin{itemize*}
    \item \pybox|'Reference:Volume'|
    \item \pybox|'Reference:Journal'|
    \item \pybox|'Reference:DOI'|
    \item \pybox|'Reference:Authors'|
    \item \pybox|'Reference:Detail'|
    \item \pybox|'Reference:Year'|
    \item \pybox|'Reference:Pages'|
    \item \pybox|'Apparatus:Kind'|
    \item \pybox|'Apparatus:Facility'|
    \item \pybox|'Apparatus:Institution'|
\end{itemize*}

@@

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for automated testing, and currently has
100\% line and branch coverage for all executable code in the repository. This
means that the tests execute every line of code at least once, and evaluate
every branch statement (e.g., if-then-else statements) to execute every condition
at least once.

Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} and
Appveyor\footnote{\url{https://ci.appveyor.com/project/Prometheus/pyked}} provide continuous
integration (CI) service for Linux, macOS, and Windows platforms. The CI services run the test suite
on every change to the source code, build and distribute binary installer packages for every
release, and build and publish the online documentation automatically. This automation ensures that
test failures are caught quickly, keeps the documentation up-to-date with the latest changes, and
streamlines the release of new versions.
